Data Preparation

### 2019-01-10 Data Preparation.Rmd
Explanation AoD Assessment
Text in #Courses Variable Engineering

Now that we have the matrix `map_assessment_AoD`, we want to find out which AoDs are covered by a course through its assessments. To do this we create an empty tibble `d_AoD_assessment` to store which assessment is covered by each course, and which AoD said assessment covers.Then, we fill in the information with a loop.
In the loop, we first extract the row of `d_assessment` and save it as `observation`. Then, we determine the corresponding assessment which we save as `assessment`. Then, we use the matrix `map_assessment_AoD` to determine which AoD `assessment` covers and use `cbind` and `rbind` to add the information to the tibble `d_AoD_assessment`.
```{r d_AoD_assessment}
d_AoD_assessment <- tibble(Code        = character(0),
                           Assessment  = character(0),
                           AoD         = character(0))

@@

### Courses
Now that we have a clear overview of the distribution of AoDs (`d_AoD`) and assessments (`d_assessment`) among the courses, let us add variables to the tibble `d_course` that contain the information at the course level. The tibble `d_ILO_detail` contains two columns indicating the code of the course and the number of ILOs it contains; `d_assessment_detail` contains three columns indicating the code of the course, the number of assessments it covers and a list of the assessments it covers; `d_AoD_detail` contains three columns indicating the code of the course, the number of AoD it covers and a list of the AoD it covers. We use a `full_join` to add these variables to the tibble `d_course`.
```{r d_course detail}
d_ILO_detail <- d_ILO %>% 
  select(Code, ILO) %>%
  distinct() %>%
  count(Code) %>%
  rename(n_ILO = n)

>>>>

Now that we have the matrix `map_assessment_AoD`, we want to find out which AoDs are covered by a course through its assessments. To do this we create an empty tibble `d_AoD_assessment` to store which assessment is covered by each course, and which AoD said assessment covers.Then, we fill in the information with a loop.
In the loop, we first extract a row of `d_assessment` and save it as `observation`. Then, we determine the corresponding assessment which we save as `assessment`. Then, we use the matrix `map_assessment_AoD` to determine which AoD `assessment` covers and use `cbind` and `rbind` to add the information to the tibble `d_AoD_assessment`.
```{r d_AoD_assessment}
d_AoD_assessment <- tibble(Code        = character(0),
                           Assessment  = character(0),
                           AoD         = character(0))

@@

### Courses
(In this section we use: `d_course`- contains information at the course-level such as in which cluster and concentration(s) they belong, and in which period(s) they are offered.)

Now that we have a clear overview of the distribution of AoDs (`d_AoD`) and assessments (`d_assessment`) among the courses, let us add variables to the tibble `d_course` that contain the information at the course level. For this we create the following three tibbles:
1) `d_ILO_detail` contains two columns indicating the code of the course and the number of ILOs it contains.
2) `d_assessment_detail` contains three columns indicating the code of the course, the number of assessments it covers and a list of the assessments it covers. 
3) `d_AoD_detail` contains three columns indicating the code of the course, the number of AoD it covers and a list of the AoD it covers. 
Then we use a `full_join` to add these variables to the tibble `d_course`.
```{r d_course detail}
d_ILO_detail <- d_ILO %>% 
  select(Code, ILO) %>%
  distinct() %>%
  count(Code) %>%
  rename(n_ILO = n)
